Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
[ paper ] more corrections.

@@

\begin{myremark}
We address proof-reconstruction in this paper for refutation proofs.
We annotate \abbre{CPL} problems using \verb!fof! formulas that
\Metis converts to \abbre{CNF} clauses to look for a refutation.
\end{myremark}

@@

Let us consider the following \TSTP derivation using
the customized \TSTP syntax. Note that we remove
empty fields in the inference information, we shorten names as long as possible, we delete the \verb!role! field when the role is
\verb!plain! and we use the ⊤, ⊥, ¬, ∧, ∨, ⇒, ⇔ symbols to express the formulas.

@@

In the following table we present the list of inference rules used
by \Metis in its \TSTP derivations for propositional logic.

We note a lack of clarity in defining the differences between the rules used in \TSTP derivations and the rules described on the documentation in
the Metis description~\cite{hurd2003first}.
These rules are not the same as we expected from the Fig.~\ref{fig:metis-inferences}.

>>>>

% \begin{myremark}
% We address proof-reconstruction in this paper for refutation proofs.
% We annotate \abbre{CPL} problems using \verb!fof! formulas that
% \Metis converts to \abbre{CNF} clauses to look for a refutation.
% \end{myremark}

@@

@@

Let us consider the following \TSTP derivation using
the customized \TSTP syntax (see the original \TSTP derivation and customizations in Appendix~\ref{app:tstp-syntax}).

@@

In the following table we present the list of inference rules used by \Metis in
the \TSTP derivations for propositional logic and reconstructed in
Section~\ref{sec:proof-reconstruction} . The reader may notice that the
inference rules presented in Fig~\ref{fig:metis-inferences} diverge from the
rules in Table~\ref{tab:agda-metis-table}. However, the former rules are
implemented by the rules in the latter. For instance, as far as we know, in
\TSTP derivations, \canonicalize, \clausify, \conjunct, and \simplify, are all
rules that represent the \emph{axiom} rule in the \Metis rules.

In the aforementioned table, we first present
the \strip inference rule since it is the rule that appears first after each
conjecture. The other rules are sorted mainly follow their level of complexity
of their definitions and the formalization presented in
Section~\ref{ssec:emulating-inferences}. Some inference rules depends the
formalizations of other rules. For instance, the \simplify rule and the
\clausify rule  need functions
developed for the \canonicalize rule. The \canonicalize rule needs functions
developed in the \resolve section. But the \resolve rule depends on the
\conjunct rule.

% We note a lack of clarity in defining the differences between the rules used in \TSTP derivations and the rules described on the documentation in
% the Metis description~\cite{hurd2003first}.
% These rules are not the same as we expected from the Fig.~\ref{fig:metis-inferences}.
